### 2019-03-06 VG500/HW0/submission.tex
HW0 done

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

@@

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Methods of Applied Mathematics I\\ HW10 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yu Cang \quad 018370210001\\ Zhiming Cui \quad 017370910006} % Your name

@@

\section{Exercise10.1}
	\begin{enumerate}
		\item
			\begin{proof}
				Since
				\begin{equation}
					\begin{aligned}
						<u, Lu> & = \int_{0}^{1} u(x) u''(x) dx\\
								& = -\Big[uu'\big|_0^1 - \int_{0}^{1}(u'(x))^2 dx\Big]\\
								& =  \int_{0}^{1}(u'(x))^2 dx \geq 0
					\end{aligned}
				\end{equation}
				Thus, the operator $L$ is positive definite.
			\end{proof}
		\item 
			\begin{proof}
				Denote $\lambda$ as the eigenvalue, and $u$ being the corresponding eigenfunction, then
				\begin{equation}
					Lu = \lambda u
				\end{equation}
				As has been proved before, the positive definite property of $L$ implies that
				\begin{equation}
					<u, Lu> = <u, \lambda u> = \lambda <u, u> = \lambda ||u||^2 \geq 0
				\end{equation}
				Thus 
				\begin{equation}
					\lambda > 0
				\end{equation}
				as the case $\lambda = 0$ is trival.\\
				Then, the solution of this ODE is 
				\begin{equation}
					u(x) = a sin(\sqrt{\lambda} x) + b cos(\sqrt{\lambda} x)
				\end{equation}
				With the B.C. at endpoints, it follows that
				\begin{equation}
					b = 0
				\end{equation}
				and
				\begin{equation}
					a(sin(\sqrt{\lambda}) + \sqrt{\lambda}cos(\sqrt{\lambda})) = 0
				\end{equation}
				Thus 
				\begin{equation}
					sin(\sqrt{\lambda}) + \sqrt{\lambda}cos(\sqrt{\lambda}) = 0
				\end{equation}
				which indicates that the eigenvalue $\lambda$ satisfies 
				\begin{equation}
					\sqrt{\lambda} = - tan(\sqrt{\lambda})
				\end{equation}
			\end{proof}
		\item 
			From the plot of $y_1(x) = -x$ and $y_2(x) = tan(x)$, the first 2 intersections in $x>0$ region lie in the gap $(\frac{1}{2}\pi, \pi)$ and $(\frac{3}{2}\pi, 2\pi)$.\\
			With the aid of MATLAB, the 2 lowest eigenvalues $\lambda_1$ and $\lambda_2$ are found as
			\begin{equation}
				\lambda_1 = (2.0288)^2 = 4.1160
			\end{equation}
			and
			\begin{equation}
				\lambda_2 = (4.9132)^2 = 24.1395
			\end{equation}
		\item 
			Denote $p(x) = a_0 + a_1 x + a_2 x^2$, the B.V. at endpoints implies that  
			\begin{equation}
				V_1 = \Big\{ p(x) | p(x) =  a_2 (x^2 - \frac{3}{2}x)\Big\}
			\end{equation}
			Thus, for any $v \in V_1$
			\begin{equation}
				\begin{aligned}
					R(v) & = \frac{<v, Lv>}{<v, v>}\\
					     & = \frac{\int_{0}^{1} a_2 (x^2 - \frac{3}{2}x) (-2a_2) dx }{\int_{0}^{1} a_2^2 (x^2 - \frac{3}{2}x)^2 dx}\\
					     & = -2\frac{\int_{0}^{1} (x^2 - \frac{3}{2}x) dx }{\int_{0}^{1} (x^2 - \frac{3}{2}x)^2 dx}\\
					     & = 4.167
				\end{aligned}
			\end{equation}
		\item 
			Denote $p(x) = a_0 + a_1 x + a_2 x^2 + a_3 x^3$, the B.V. at endpoints implies that  
			\begin{equation}
				V_2 = \Big\{ p(x) | p(x) =  a_2 (x^2 - \frac{3}{2}x) + a_3 (x^3 - 2x)\Big\}
			\end{equation}
			Thus, for any $v \in V_2$
			\begin{equation}
				\begin{aligned}
					R(v) & = \frac{<v, Lv>}{<v, v>}\\
						& = \frac{\int_{0}^{1} [a_2 (x^2 - \frac{3}{2}x) + a_3(x^2 - 2 x)][2a_2 + 6a_3 x] dx }{\int_{0}^{1} [a_2 (x^2 - \frac{3}{2}x) + a_3(x^2 - 2 x)]^2 dx}\\
						& = \frac{175a_2^2 + 630a_2a_3 + 588a_3^2}{42a_2^2 + 154a_2a_3 + 142a_3^2}
				\end{aligned}
			\end{equation}
			As the leading coefficient $a_3\neq 0$, then, denote $t \triangleq \frac{a_2}{a_3}$
			\begin{equation}
				R(v) = \frac{175t^2 + 630 t + 588}{42t^2 + 154t + 142}
			\end{equation}
			It's obvious that $R(v)$ goes to its minimal when $t \rightarrow \infty$, thus $\min R(v) = \frac{175}{42}=4.1667$.
		\item 
			Firstly, determine the general form of each element $v \in V_3$.\\
			Denote $v(x) = a_2 (x^2 - \frac{3}{2}x) + a_3 (x^3 - 2x)$ as $v \in V_2$, then, as $v$ also lies in $V_1^\perp$, it means
			\begin{equation}
				\int_{0}^{1} (x^2 - \frac{3}{2}x) v(x) dx = 0
			\end{equation}
			namely
			\begin{equation}
				a_2 \int_{0}^{1} (x^2 - \frac{3}{2}x)^2 dx + a_3 \int_{0}^{1} (x^2 - \frac{3}{2}x)(x^3 - 2x) dx = 0
			\end{equation}
			Thus
			\begin{equation}
				a_2 = - \frac{16}{3} a_3
			\end{equation}
			Hence
			\begin{equation}
				v(x) = a_3(x^3 - \frac{16}{3}x^2 + 6x)
			\end{equation}
			and
			\begin{equation}
				v''(x) = a_3(6x - \frac{32}{3})
			\end{equation}
			Thus, for any $v \in V_3$, the second eigenvalue is estimated as
			\begin{equation}
				\begin{aligned}
					R(v) & = \frac{<v, Lv>}{<v, v>}\\
						& = -\frac{\int_{0}^{1} (x^3 - \frac{16}{3}x^2 + 6x)(6x - \frac{32}{3}) dx }{\int_{0}^{1} (x^3 - \frac{16}{3}x^2 + 6x)^2 dx}\\
						& = 4.2803
				\end{aligned}
			\end{equation}
	\end{enumerate}

>>>>

@@

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Technical Communication\\ HW0 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Author: Yu Cang \quad 018370210001\\ Partner: Guiwen Tan \quad 118370910014} % Your name

@@

\section{Summary of Yu Cang's  research project}
	Currently, my research focus on numerical simulation of the one-dimensional  counter-flow diffusion flame.\\
	Numerical schemes play an important role in solving this problem as proper schemes have better convergence performance. \\
	Generally speaking, a hybrid scheme consists of the damped Newton method and the semi-implicit time stepping scheme is used.\\
	At the beginning, I try to solve the steady-state equation set with the damped Newton method, once the newton iteration fails, it turns to solve the time-dependent equation set. In this way,  a new starting estimation can be provided for the next trial of the newton method.

\section{Paraphrase of Guiwen Tan's work}
	A wide range of spatial and temporal scales exist in a turbulence field and they interact with each other.\\
	The spatial structure at different scales is the focus of his reseach. In order to show the spatial structures at different levels, the multi-level segment analysis(MSA) method is adopted.\\
	At present, he uses the sinusoidal function, fractional Brownain motion, and DNS result of real turbulence field to verify the MSA method. The statistical characteristics of each testing case indicates if the MSA method is justified.

\section{Improved Version of Yu Cang's work}
	The configuration of one-dimensional counter-fow diffusion flame involves a burning chamber and two opposing placed inlents, where fuel and oxdizer are pumped into the chamber. A flame front burning in between is sustained, and that is counter-flow diffusion flame.\\
	My research mainly focus on the numerical simulation of the one-dimensional counter-flow diffusion flame. Numerical method should be choosen carefully as some of schemes may converge faster and better. \\
	Usually, I use the damped Newton method and the semi-implicit time stepping scheme in numerical simulation. At first, I use the damped Newton method to deal with steady-state equation set. Once the damped Newton method fails or diverges, I switch to the time-dependent equation set with the semi-implicit time stepping scheme. In this way,  results from the time-dependent equation set can provide a new starting estimation for the newton method of next step.
